---
title: "Codebook: Getting and cleaning data, Peer-graded assignment"
output: html_notebook
---
# Assignment by Milena

# 

In order to create the final tidy data set as required in the assignment, I had 
to first install a package called "dplyr" because it provides some tools for 
better handling datasets in R.

When I downloaded the dataset, I saw that there were couple of files that should be further extracted and merged as described in the assignment: 
1. features.txt (accelerometer and gyroscope signals data)
2. activity_labels.text (list of activities and codes)
3. subject_test.txt (volunteers test data)
4. X_test.txt (recorded features test data)
5. Y_test.txt (test data of activities code)
6. subject_train.txt (train data)
7. X_train.txt (recorded features train data)
8. Y_train.txt (train data of activites code)

# 1.step 
The first step of this assignment is to merge both the training and the test 
datasets and then to create one merged file. I used the functions rbind and cbind
to perform this action 
```{r}
Xtrainandtest <- rbind(x_train, x_test)
Ytrainandtest <- rbind(y_train, y_test)
Subjecttraintest <- rbind(subject_train, subject_test)
Merging_Data <- cbind(Subjecttraintest, Ytrainandtest, Xtrainandtest)
```
I got 4 new merged files 
- Xtrainandtest (10299rows, 561 columns)
- Ytrainandtest (10299rows, 1 column)
- Subjecttraintest (10299rows, 1 column)
- Merging_Data (10299rows, 563 columns)

# 2.step
The second step of the assignment is to extract only the measurements on the mean and standard deviation for each measurement.

```{r}
TidyData <- Merging_Data %>% select(subject, code, contains("mean"), contains("std"))
```

In fact, it is done by subsetting the Merging_Data and selecting only certain columns: "subject", "code", measurements of the mean "mean" and measurements of the standard deviation "std".

# 3.step
The third step of the assignment is to use descriptive names to name the activities in the data set:

```{r}
TidyData$code <- activities[TidyData$code, 2]
```



# 4. step
The fourth step of the assignment is to label appropriately the data set 
with descriptive variable names. It means that  numbers in the 
column "code" have to be replaced with appropriate values from the "activity" second column:

```{r}
names(TidyData)[2] = "activity"
names(TidyData)<-gsub("Acc", "Accelerometer", names(TidyData))
names(TidyData)<-gsub("Gyro", "Gyroscope", names(TidyData))
names(TidyData)<-gsub("BodyBody", "Body", names(TidyData))
names(TidyData)<-gsub("Mag", "Magnitude", names(TidyData))
names(TidyData)<-gsub("^t", "Time", names(TidyData))
names(TidyData)<-gsub("^f", "Frequency", names(TidyData))
names(TidyData)<-gsub("tBody", "TimeBody", names(TidyData))
names(TidyData)<-gsub("-mean()", "Mean", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-std()", "STD", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-freq()", "Frequency", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("angle", "Angle", names(TidyData))
names(TidyData)<-gsub("gravity", "Gravity", names(TidyData))
```




# 5.step
The fifth step of the assignment is to use the data set from step 4 to create 
a second, new independent tidy data set with the average of each variable for each activity and each subject:

```{r}
NewTidyData <- TidyData %>%
  group_by(subject, activity) %>%
  summarise_all(funs(mean))
write.table(NewTidyData, "NewTidyData.txt", row.name=FALSE)
```

Finally,  I exported the tidy data set into NewTidyData.txt file/




